Proposed Solution

### 2016-11-14 Ennan-Proposal/impact.tex

>>>>

Since her beginning of teaching at Yale, the PI is actively including topics from her 
research into her courses (such as ``Software Analysis and Verification''). This way
she motivates undergraduate students to get involved in the research. Until now 
she supervised more than 20 undergraduate student projects. Two students (Reinking, Cai) 
who did an undergraduate research projects with her, are now PhD students at 
UC Berkeley, and two more students are applying (Anklessaria, La) to graduate schools 
this year. Additionally, there are two student startups, which are now supported
by YCombinator, that started under her supervision. Those startup are PatientBank
and Py, an app for learning Python. Some

The PI will continue to involve the undergraduate student into 
this project as well, spreading this way the project ideas to a broader community.
In addition, we plan to disseminate the results via publications and giving talks 
to the communities of PL/Verification researchers and System researchers.
